---
title: "p8105_hw1_jq2342"
output: github_document
date: "2022-09-22"
---


**QUESTION 1**
```{r dfpenguins}
library(tidyverse)
data("penguins", package = "palmerpenguins")
df=penguins
ls(df)
nrow(df) 
ncol(df)
mean(df$flipper_length_mm, na.rm=TRUE)
```
##1. The penguins data includes the species, island, length and depth of the bill, length of the flippers, body mass, sex and year.
##2. There are 8 variables(column) and 344 observations(row)
##3. The mean for flipper_length_mm is 200.9152

```{r scatterplot}

ggplot(df, aes(x=bill_length_mm, y=flipper_length_mm, color=species,na.rm=TRUE)) + geom_point(na.rm=TRUE)
ggsave("df.png")
```

**QUESTION 2**
```{r  createdf}
hw1_df=tibble (  
vec_ran=rnorm(n=10),
vec_logi=vec_ran>0,
vec_char=(c("this", "is", "a", "character", "vector", "for", "the", "home", "work", "two")),
vec_fac=factor(c("one","two","three","one","two","three","one","two","three","one"))
)
```

```{r mean}
mean(hw1_df$vec_ran, na.rm=TRUE)
mean(hw1_df$vec_logi, na.rm=TRUE)
mean(hw1_df$vec_char, na.rm=TRUE)
mean(hw1_df$vec_fac, na.rm=TRUE)
```
##the mean of vec_ran is 0.152
##the mean of vec_logi is 0.3, there should not be a mean for the logical since true and false do not have numeric value, however r treats TRUE as 1 and FALSE as 0.
##the mean of vec_char is not applicable because character variable doesn' have a numeric value 
##the mean of vec_fac is not applicable because string variable doesn' have a numeric value 

```{r asnumericfunction}
hw1_df$vec_char = as.numeric(as.character(hw1_df$vec_char)) 
hw1_df$vec_logi = as.numeric(as.character(hw1_df$vec_logi)) 
hw1_df$vec_fac = as.numeric(as.character(hw1_df$vec_fac)) 
print (sapply(hw1_df, class))
```
##after applying as.numeric to the non-numeric variables, they are changed into numeric variables.This explain why the mean for those variable are not applicable since they weren't numeric













